---
title: "Autisitic Adults in Oregon"
output: html_notebook
---

The Oregon Department of Disability Services (ODDS) reported that the agency was serving 22,984 adults with an intellectual or developmental disability in 2023. A 2021-2022 survey by ODDS and along with the National Core Indicatargetrs (NCI) project showed that 6,435 (28%) of Oregon adults receiving I/DD services had an Autism diagnosis. The US Census estimates that in 2022 there were roughly 3,404,221 adults (18+) in Oregon. A CDC study (2020) estimated that in 2017, 2.28% (95% CI [1.83, 2.8]) of Oregon adults had Autism; in numbers: 77,616 (95% CI [62,297, 95,318]). (Numbers courtesy of Jon Saitarget, Oregon Council on Autism Spectrum Disorder)

Census Bureau: https://data.census.gov/table/ACSST1Y2022.S0101?q=oregon%20population%20by%20age

>=18 3407770

ODDS 2023: https://olis.oregonlegislature.gov/liz/2023R1/Downloads/CommitteeMeetingDocument/260382

22,755 adults


https://acl.gov/iddcounts


CDC Report prevalence of autism in Oregon https://stacks.cdc.gov/view/cdc/119183
2.28%

```{r}
library(tidyverse)
library(ggplot2)
```

# Raw Data
```{r}
us_census_or_18_plus = 3407770
cdc_pct_autisitc_adults = list(number=2.23, low_95_ci=1.83, high_95_ci=2.8)
or_adults_idd = 22755
or_adults_idd_pct_autistic = 28
or_adults_idd_autistic = 6435 ### 28%
```



```{r}
csv_data="
Category,Number,low,high
Adults Receiving I/DD Service,22984,NA,NA
Autistic Adults Receiving I/DD Services,6435,NA,NA
Autistic Adults,77616,62297,95318
"

data =
  tibble(
    category = c(
      "Adults Receiving I/DD Service",
      "Autistic Adults Receiving I/DD Services",
      "Adults",
      "Autistic Adults (CDC estimate)"
    ),
    number = c(
      22984,
      6435,
      us_census_or_18_plus,
      us_census_or_18_plus*cdc_pct_autisitc_adults$number/100
    ),
    low = c(
      NA, NA, NA,
      us_census_or_18_plus*cdc_pct_autisitc_adults$low_95_ci/100
    ),
    high = c(
      NA, NA, NA,
      us_census_or_18_plus*cdc_pct_autisitc_adults$high_95_ci/100
    ),
    color = c("#E66100", "#D5A6BD", "#E1BE6A", "#40B0A6")
  ) %>%
  mutate(number = round(number))

data %>% filter(category != "Adults") %>%
  ggplot(aes(x=category, y=number, fill=color)) +
  geom_bar(stat = "identity") +
  scale_x_discrete(limit=rev(c("Autistic Adults (CDC estimate)", "Adults Receiving I/DD Service", "Autistic Adults Receiving I/DD Services"))) +
  geom_errorbar(
    aes(x=category, ymin=low, ymax=high),
    width=0.2, color="black",
    size=1
  ) +
  geom_text(aes(label = number), hjust = -0.2, vjust=-0.5, color="black") +
  labs(y="Population", x=NULL) +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size=12, face="bold"), # Adjust font size and font-weight for y-axis labels
    axis.title.y = element_text(size=12, face="bold") # Optionally, adjust font size and font-weight for y-axis title
  ) +
  coord_flip()


custom_colors = c(
  "Adults Receiving I/DD Service" = "#E66100",
  "Autistic Adults Receiving I/DD Services" = "#D5A6BD",
  "Adults" = "#E1BE6A",
  "Autistic Adults (CDC estimate)" = "#40B0A6"
)

```


https://acl.gov/grants/open-opportunities
https://acl.gov/iddcounts
https://legacy.nationalcoreindicatargetrs.org/upload/core-indicatargetrs/OR_IPS_state_508.pdf
https://www.advancingstates.org/

```{r}
N_adults = us_census_or_18_plus
# N_adults = 1000
N_autistic = round(N_adults*cdc_pct_autisitc_adults$number/100)
N_receiving_idd = round(N_adults*or_adults_idd/us_census_or_18_plus)
N_receiving_idd_autistic = round(N_receiving_idd*or_adults_idd_pct_autistic/100)
N_receiving_idd_not_autistic = N_receiving_idd - N_receiving_idd_autistic

adults = 1:N_adults
autistic = sample(adults, N_autistic, replace=F)
not_autistic = setdiff(adults, autistic)
receiving_idd_not_autistic = sample(not_autistic, N_receiving_idd_not_autistic, replace=F)
receiving_idd_autistic = sample(autistic, N_receiving_idd_autistic, replace=F)
receiving_idd = c(receiving_idd_autistic, receiving_idd_not_autistic)

data = list(
  adults = adults,
  autisitc = autistic,
  receiving_idd = receiving_idd,
  receiving_idd_autistic = receiving_idd_autistic
)

library(grid)
library(VennDiagram)
# library(cowplot)


overrideTriple = TRUE
vd = draw.triple.venn(
    area1=N_adults, area2=N_autistic, area3=N_receiving_idd,
    n12=N_autistic, n23=N_receiving_idd_autistic, n13=N_receiving_idd,
    n123=N_receiving_idd_autistic,
    category=c("Adults in Oregon","Autistic","Receiving I/DD Services"),
    col="Black",fill=c("White","Red","Yellow"),
    cex=3, cat.cex=2,
    euler.d=TRUE, scaled=TRUE
  )
grid.newpage()
grid.draw(vd)
```

```{r}
N_people = 12
N_orgs = 5

items = tibble(
  item = str_glue("item_{1:(N_people + N_orgs)}"),
  type = c(rep("person", N_people), rep("org", N_orgs)),
)

edges = tibble(source = character(), target = character())
N_people_connections = 6
N_org_connections = 2
N_org_people_connections = 5

ids = items$item
people = items %>% filter(type=="person") %>% pull(item)
orgs = items %>% filter(type=="org") %>% pull(item)

for (i in 1:N_people_connections)
{
  person_1 = sample(people, 1)
  person_2 = sample(setdiff(people, person_1), 1)
  print(str_glue("person 1: {person_1}, person 2: {person_2}"))
  edges =
    edges %>%
    add_row(source=person_1, target=person_2)
}

for (i in 1:N_org_connections)
{
  org_1 = sample(orgs, 1)
  org_2 = sample(setdiff(orgs, org_1), 1)
  print(str_glue("org 1: {org_1}, org 2: {org_2}"))
  edges =
    edges %>%
    add_row(source=org_1, target=org_2)
}

for (i in 1:N_org_people_connections)
{
  item_1 = sample(orgs, 1)
  item_2 = sample(people, 1)
  print(str_glue("item 1: {item_1}, item 2: {item_2}"))
  edges =
    edges %>%
    add_row(source=item_1, target=item_2)
}
```

```{r}
library(igraph)

items = read_csv("items.csv")
edges = read_csv("edges.csv")

g = graph_from_data_frame(
  d = edges,
  vertices = items,
  directed = FALSE
)

V(g)$type <- items$type[match(V(g)$name, items$item)]

library('png')

person_img <- readPNG("person.png")
org_img <- readPNG("building2.png")

# Assign raster attributes to nodes
V(g)$raster <- lapply(V(g)$type, function(x) if (x == "person") person_img else org_img)

plot(g,
  vertex.shape="raster",
  # vertex.label=type,
  vertex.size=10,
  vertex.size2=10,
  edge.width=5
)


# node_colors <- ifelse(V(g)$type == "person", "blue", "red")
#
# plot(g,
#   vertex.color = node_colors,
#   vertex.size = 20,
#   vertex.label.color = "black",
#   vertex.label.cex = 0.8,
#   main = "Network Visualization"
# )

```

```{r}

# Create the items table
items <- tibble(
  item = c("item_1", "item_2", "item_3", "item_4"),
  type = c("person", "org", "person", "org")
)

# Create the edges table
edges <- tibble(
  from = c("item_1", "item_2", "item_3"),
  to = c("item_2", "item_3", "item_4")
)

# Convert to data frames for igraph
items_df <- as.data.frame(items)
edges_df <- as.data.frame(edges)

g <- graph_from_data_frame(d = edges_df, vertices = items_df, directed = FALSE)

# Add node attributes (type)
V(g)$type <- items_df$type[match(V(g)$name, items_df$item)]

# Define shapes for node types
node_shapes <- ifelse(V(g)$type == "person", "square", "circle")

# Define colors for node types
node_colors <- ifelse(V(g)$type == "person", "blue", "red")

# Plot the network with built-in shapes
plot(g, vertex.shape = node_shapes, vertex.color = node_colors, vertex.size = 20, vertex.label.color = "black",
     vertex.label.cex = 0.8, main = "Network Visualization with Built-in Shapes")

```
```{r}
counts = c(
  A = 100,
  B = 20,
  C = 10,
  "A&B" = 20,
  "A&C" = 10,
  "B&C" = 3,
  "A&B&C" = 3
)

N_adults = us_census_or_18_plus
# N_adults = 1000
N_autistic = round(N_adults*cdc_pct_autisitc_adults$number/100)
N_receiving_idd = round(N_adults*or_adults_idd/us_census_or_18_plus)
N_receiving_idd_autistic = round(N_receiving_idd*or_adults_idd_pct_autistic/100)
N_receiving_idd_not_autistic = N_receiving_idd - N_receiving_idd_autistic

counts = c(
  "Adults" = N_adults,
  "Autistic" = N_autistic,
  "Receiving I/DD" = N_receiving_idd,
  "Adults&Autistic" = N_autistic,
  "Adults&Receiving I/DD" = N_receiving_idd,
  "Autistic&Receiving I/DD" = N_receiving_idd_autistic,
  "Adults&Autistic&Receiving I/DD" = N_receiving_idd_autistic
)

library(eulerr)

counts = c(
  "Adults" = 3407770,
  "Autistic" = 75993,
  "Receiving I/DD" = 22755,
  "Adults&Autistic" = 75993,
  "Adults&Receiving I/DD" = 22755,
  "Autistic&Receiving I/DD" = 6371,
  "Adults&Autistic&Receiving I/DD" = 6371
)

plot(
  x = euler(counts, input="union", shape="ellipse"),
  quantities = T,
  legend = list(
    labels = list(
      str_glue("Adults: {N_adults}"),
      str_glue("Autistic: {N_autistic}"),
      str_glue("Receiving I/DD: {N_receiving_idd}")
    ),
    col="black",
    font=10
  ),
  labels = F,
  adjust_labels = T,
  main = "Oregon Autistic Adults and Receiving I/DD",
  fills = list("#e1be6a", "#40B0A6", "#E66100")
)

# Create the Euler diagram
fit <- euler(counts, input="union", shape="ellipse")

# Plot the Euler diagram with specified parameters
plot(
  x = fit,
  quantities = list(fontfamily = "Helvetica"), # Set font for quantities
  legend = list(
    labels = c(
      str_glue("Adults: {counts['Adults']}"),
      str_glue("Autistic: {counts['Autistic']}"),
      str_glue("Receiving I/DD: {counts['Receiving I/DD']}"),
      str_glue("Autistic&Receiving I/DD: {counts['Autistic&Receiving I/DD']}")
    ),
    col = "black",
    font = 10,
    fontfamily = "Helvetica" # Set font for legend
  ),
  fills = c("#e1be6a", "#40B0A6", "#E66100"), # Apply fill colors
  labels = F,
  adjust_labels = T,
  main = list(
    label = "Oregon Autistic Adults and Receiving I/DD",
    fontfamily = "Times New Roman" # Set font for title
  )
)

# Add custom legend separately for fine control
legend("topright", legend = c(
  str_glue("Adults: {counts['Adults']}"),
  str_glue("Autistic: {counts['Autistic']}"),
  str_glue("Receiving I/DD: {counts['Receiving I/DD']}"),
  str_glue("Autistic&Receiving I/DD: {counts['Autistic&Receiving I/DD']}")
), fill = c("#e1be6a", "#40B0A6", "#E66100"), bty = "n", cex = 0.8,
       text.font = 2, text.col = "black", inset = 0.05,
       text.family = "Helvetica") # Set font for custom legend
```


```{r}
library(tidyverse)
library(eulerr)
library(sysfonts)
library(showtext)
library(systemfonts)

font_add("Times New Roman", regular = "C:/Windows/Fonts/times.ttf")
font_add("Helvetica", regular = "C:/Windows/Fonts/arial.ttf") # Use Arial as a substitute for Helvetica

# Enable showtext for text rendering
showtext_auto()



counts = c(
  "Adults" = 3407770,
  "Autistic" = 75993,
  "Receiving I/DD" = 22755,
  "Adults&Autistic" = 75993,
  "Adults&Receiving I/DD" = 22755,
  "Autistic&Receiving I/DD" = 6371,
  "Adults&Autistic&Receiving I/DD" = 6371
)

# Create the Euler diagram
fit <- euler(counts, input="union", shape="ellipse")
# Define custom colors for sets and intersections
custom_colors <- c(
  "Adults" = "#e1be6a",
  "Autistic" = "#40B0A6",
  "Receiving I/DD" = "#E66100",
  "Adults&Autistic" = "#A1C4A6",       # Custom color for Adults & Autistic intersection
  "Adults&Receiving I/DD" = "#F4A582",  # Custom color for Adults & Receiving I/DD intersection
  "Autistic&Receiving I/DD" = "#92C5DE", # Custom color for Autistic & Receiving I/DD intersection
  "Adults&Autistic&Receiving I/DD" = "#D5A6BD" # Custom color for the triple intersection
)
```


```{r}
library(tidyverse)
library(eulerr)
library(sysfonts)
library(showtext)
library(systemfonts)

# Load fonts
font_add("Times New Roman", regular = "C:/Windows/Fonts/times.ttf", bold = "C:/Windows/Fonts/timesbd.ttf")
font_add("Helvetica", regular = "C:/Windows/Fonts/arial.ttf", bold = "C:/Windows/Fonts/arialbd.ttf") # Substitute Arial for Helvetica
showtext_auto()

# Define counts for the Euler diagram
counts = c(
  "Adults" = 3407770,
  "Autistic" = 75993,
  "Receiving I/DD" = 22755,
  "Adults&Autistic" = 75993,
  "Adults&Receiving I/DD" = 22755,
  "Autistic&Receiving I/DD" = 6371,
  "Adults&Autistic&Receiving I/DD" = 6371
)

# Create the Euler diagram
fit <- euler(counts, input = "union", shape = "ellipse")

# Define custom colors for sets and intersections
custom_colors <- c(
  "Adults" = "#e1be6a",
  "Autistic" = "#40B0A6",
  "Receiving I/DD" = "#E66100",
  "Adults&Autistic" = "#A1C4A6",       # Custom color for Adults & Autistic intersection
  "Adults&Receiving I/DD" = "#F4A582",  # Custom color for Adults & Receiving I/DD intersection
  "Autistic&Receiving I/DD" = "#92C5DE", # Custom color for Autistic & Receiving I/DD intersection
  "Adults&Autistic&Receiving I/DD" = "#D5A6BD" # Custom color for the triple intersection
)

plot.new()
# Plot the Euler diagram with specified parameters
plot(
  x = fit,
  # quantities = list(fontfamily = "Helvetica"), # Set font for quantities
  fills = custom_colors,
  labels = F,
  main = list(
    label = "Oregon Autistic Adults and Receiving I/DD",
    fontfamily = "Helvetica", # Set font for title
    fontsize = 12
  )
)

# Set font family for the legend
par(family = "Helvetica")
# par(mar = c(5, 4, 6, 2))  # bottom, left, top, right

legend_strings = map(
    names(counts)[c(1,2,3,5)],
    ~
      str_glue("{.x}: {format(counts[.x], nsmall=0, big.mark=',')}") %>%
      str_replace("&", " & ")
  )

legend(
  "topright",
  inset = c(0.25, -0.06),
  legend = legend_strings,
  fill = c("#e1be6a", "#40B0A6", "#E66100", "#D5A6BD"),
  bty = "n",
  cex = 1,
  text.font = 1,
  text.col = "black",

)

# title(
#   main = "Oregon Autistic Adults and Receiving I/DD",
#   family = "Helvetica",
#   font.main = 2,
#   cex.main = 2,
#   line = 2
# )

```


```{r}
library(VennDiagram)
# Define the counts
counts <- c(
  "Adults" = 3407770,
  "Autistic" = 75993,
  "Receiving I/DD" = 22755,
  "Adults&Autistic" = 75993,
  "Adults&Receiving I/DD" = 22755,
  "Autistic&Receiving I/DD" = 6371,
  "Adults&Autistic&Receiving I/DD" = 6371
)

# Create the Venn diagram
venn.plot <- draw.triple.venn(
  area1 = counts["Adults"],
  area2 = counts["Autistic"],
  area3 = counts["Receiving I/DD"],
  n12 = counts["Adults&Autistic"],
  n23 = counts["Autistic&Receiving I/DD"],
  n13 = counts["Adults&Receiving I/DD"],
  n123 = counts["Adults&Autistic&Receiving I/DD"],
  category = c("Adults", "Autistic", "Receiving I/DD"),
  fill = c("#FFDDC1", "#99DDFF", "#FFCC99"),
  lty = "blank",
  cex = 2,
  cat.cex = 2,
  cat.col = c("#FF5733", "#33FF57", "#3357FF"),
  cat.pos = c(-20, 20, 180),
  cat.dist = c(0.05, 0.05, 0.05)
)
grid.draw(venn.plot)


```


```{r}
library(ggvenn)
# Define the counts
counts <- c(
  "Adults" = 3407770,
  "Autistic" = 75993,
  "Receiving I/DD" = 22755,
  "Adults&Autistic" = 75993,
  "Adults&Receiving I/DD" = 22755,
  "Autistic&Receiving I/DD" = 6371,
  "Adults&Autistic&Receiving I/DD" = 6371
)

# Convert counts to a list of sets
sets <- list(
  Adults = seq(1, counts["Adults"]),
  Autistic = seq(1, counts["Autistic"]),
  Receiving_IDD = seq(1, counts["Receiving I/DD"])
)

# Create the Venn diagram
ggvenn(sets, c("Adults", "Autistic", "Receiving_IDD"), fill_color = c("#FFDDC1", "#99DDFF", "#FFCC99"))

```

```{r}
library(ggVennDiagram)
# Define the counts
counts <- c(
  "Adults" = 3407770,
  "Autistic" = 75993,
  "Receiving I/DD" = 22755,
  "Adults&Autistic" = 75993,
  "Adults&Receiving I/DD" = 22755,
  "Autistic&Receiving I/DD" = 6371,
  "Adults&Autistic&Receiving I/DD" = 6371
)

# Prepare a list of sets representing each category
venn_data <- list(
  Adults = seq_len(counts["Adults"]),
  Autistic = seq_len(counts["Autistic"]),
  "Receiving_I/DD" = seq_len(counts["Receiving I/DD"])
)

# Create the Venn diagram
ggVennDiagram(venn_data, set_names = names(venn_data)) +
  scale_fill_gradient(low = "#F4A582", high = "#92C5DE") +
  theme_void() +
  theme(legend.position = "none")


```

```{r}
library(venn)

# Define the counts
counts <- c(
  "Adults" = 3407770,
  "Autistic" = 75993,
  "Receiving I/DD" = 22755,
  "Adults&Autistic" = 75993,
  "Adults&Receiving I/DD" = 22755,
  "Autistic&Receiving I/DD" = 6371,
  "Adults&Autistic&Receiving I/DD" = 6371
)

# Create a data frame for the counts
venn_data <- data.frame(
  Adults = c(TRUE, TRUE, TRUE, TRUE, FALSE, FALSE, FALSE),
  Autistic = c(TRUE, TRUE, FALSE, TRUE, TRUE, FALSE, FALSE),
  Receiving_IDD = c(TRUE, FALSE, TRUE, TRUE, TRUE, TRUE, FALSE),
  Counts = c(counts["Adults&Autistic&Receiving I/DD"], 
             counts["Adults&Autistic"] - counts["Adults&Autistic&Receiving I/DD"], 
             counts["Adults&Receiving I/DD"] - counts["Adults&Autistic&Receiving I/DD"], 
             counts["Autistic&Receiving I/DD"] - counts["Adults&Autistic&Receiving I/DD"], 
             counts["Autistic"] - counts["Adults&Autistic"] - counts["Autistic&Receiving I/DD"] + counts["Adults&Autistic&Receiving I/DD"], 
             counts["Receiving I/DD"] - counts["Adults&Receiving I/DD"] - counts["Autistic&Receiving I/DD"] + counts["Adults&Autistic&Receiving I/DD"], 
             counts["Adults"] - counts["Adults&Autistic"] - counts["Adults&Receiving I/DD"] + counts["Adults&Autistic&Receiving I/DD"])
)

# Create the Venn diagram
venn_obj <- venn(venn_data, z = venn_data$Counts)

# Plot the Venn diagram
plot(venn_obj)

```
```{r}
library(vcd)

# Define the counts
counts <- c(
  "Adults" = 3407770,
  "Autistic" = 75993,
  "Receiving I/DD" = 22755,
  "Adults&Autistic" = 75993,
  "Adults&Receiving I/DD" = 22755,
  "Autistic&Receiving I/DD" = 6371,
  "Adults&Autistic&Receiving I/DD" = 6371
)

# Create a data frame for the mosaic plot
data <- data.frame(
  Adults = c("Yes", "Yes", "Yes", "Yes", "No", "No", "No"),
  Autistic = c("Yes", "Yes", "No", "Yes", "Yes", "No", "No"),
  Receiving_IDD = c("Yes", "No", "Yes", "Yes", "Yes", "Yes", "No"),
  Counts = c(
    counts["Adults&Autistic&Receiving I/DD"], 
    counts["Adults&Autistic"] - counts["Adults&Autistic&Receiving I/DD"], 
    counts["Adults&Receiving I/DD"] - counts["Adults&Autistic&Receiving I/DD"], 
    counts["Autistic&Receiving I/DD"] - counts["Adults&Autistic&Receiving I/DD"], 
    counts["Autistic"] - counts["Adults&Autistic"] - counts["Autistic&Receiving I/DD"] + counts["Adults&Autistic&Receiving I/DD"], 
    counts["Receiving I/DD"] - counts["Adults&Receiving I/DD"] - counts["Autistic&Receiving I/DD"] + counts["Adults&Autistic&Receiving I/DD"], 
    counts["Adults"] - counts["Adults&Autistic"] - counts["Adults&Receiving I/DD"] + counts["Adults&Autistic&Receiving I/DD"]
  )
)

# Create a table from the data frame
data_table <- xtabs(Counts ~ Adults + Autistic + Receiving_IDD, data = data)

# Create the mosaic plot
mosaic(data_table, shade = TRUE, legend = TRUE)
```


